On the numerical stability of static Gaussian wave packets

### 2018-01-08 jcp-0-0.tex
start drafting the static wave packets paper

\begin{abstract}
% insert abstract here
\end{abstract}

@@

>>>>

\begin{abstract}
The ability to expand high-energy states over a set of non-orthogonal wave packets causes the wave packet equations of motion to become stiff.  On the other hand, a dense set of wave packets is required to have stable expansions of wave functions.  Tychonov regularisation of the expansion operator suppresses the energies of the high-energy states, while retaining all the physics that happens slower than a given time scale.
\end{abstract}

@@

Schemes such as \cite{jcp-132-244111,jcp-136-014109} have used moving grids of coherent states, to which all these considerations would apply.
